COG-ED Manuscript

### 2022-01-17 06_Paper/COG-ED/Manuscript.Rmd
shortened the results section a lot

---
title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1,*"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1,*"
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
      - Visualization
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
  * Shared first authorship
abstract: |
  When individuals set goals, they consider the subjective value (SV) of both the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  However, the SV of effort is highly individual, and previous quantification approaches have had two crucial limitations: They presumed a unidirectional relationship between objective task load and the SV of effort, and as a consequence, they could only quantify the SVs of tasks with an objective order of task load.
  One of these approaches is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013).
  We aim to replicate their analysis with our adaptation, the Cognitive and Emotion Regulation Effort Discounting (CERED) paradigm.
  We argue that the CERED paradigm allows two crucial things: Quantifying SVs without assuming that the easiest level is preferred, and quantifying SVs for tasks with no objective order of task load.

@@

Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013], and detailed in the attached design table..
Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing n-back level, (1b) reaction time increases with increasing n-back level, and (1c) perceived task load increases with n-back level.
Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
Here we added they hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.

@@

The results of each analysis will be assessed on the basis of both *p*-value and the Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021].

@@

We collected data from $N = 16$ participants,
One participant's NASA-TLX data is incomplete due to a technical error, so hypotheses 1c and 3b are analyzed using the 15 complete data sets.
Contrary to our expectations, the rmANOVA revealed no decrease in performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_rmanova)$full_result`).

@@

However, RTs increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
RTs were longer for 3- than 2-back (`r apa_print(pairs(emmeans(object = hypothesis1b_rmanova$aov,specs = "level")))[1]`), but not different between 2- and 4-back or 3- and 4-back.
Even though *d'* did not decrease, the increases in RT indicate an increase in objective task load.

@@

Increases in subjective task load were investigated for each NASA-TLX subscale, now including 1-back.
Ratings on the mental load and effort subscales increased between all n-back levels ($p<.001$) except between 3- and 4-back.
Ratings on the physical load and the performance subscales only differed between 1- and 3-back (`r apa_print(pairs(emmeans(object = hypothesis1c_physical_rmanova$aov,specs = "level")))$statistic$X1_X3`, and `r apa_print(pairs(emmeans(object = hypothesis1c_performance_rmanova$aov,specs = "level")))$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(pairs(emmeans(object = hypothesis1c_physical_rmanova$aov,specs = "level")))$statistic$X1_X4`, and `r `apa_print(pairs(emmeans(object = hypothesis1c_performance_rmanova$aov,specs = "level")))$statistic$X1_X4`, respectively).
Ratings on the frustration and time pressure subscales increased between all n-back levels ($p<.001$) except between 1- and 2-back and 3- and 4-back.
Overall, these ratings showed that the increase in task load was being perceived as such.

@@

The rmANOVA indicated significant differences between SVs depending on n-back level (`r apa_print(hypothesis2a_rmanova)$full_result`).
SVs were higher for 1- than 3-back (`r apa_print(pairs(emmeans(object = hypothesis2a_rmanova$aov,specs = "level")))$statistic$X1_X3`), for 1- than 4-back (`r apa_print(pairs(emmeans(object = hypothesis2a_rmanova$aov,specs = "level")))$statistic$X1_X4`), and for 2- than 4-back (`r apa_print(pairs(emmeans(object = hypothesis2a_rmanova$aov,specs = "level")))$statistic$X2_X4`).
Importantly, the lack of difference between the SVs of 1- and 2-back indicates that when given the choice, not all participants preferred the easiest level.
This can be considered preliminary proof-of-concept, as this behavioural pattern can only emerge in the CERED paradigm, but not in the original COG-ED paradigm.

@@

  # save plot
  h2c_jn.plot <- h2c_jn$plot

  # create interaction plot
  h2c_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                               plot.points = T, point.shape = T,
                               x.label = "n-back level", y.label = "subjective value",
                               legend.main = "NFC", interval = T) + theme_apa() +
    scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))

@@

The MLM revealed that n-back level was a reliable predictor of SV (`r apa_print(m1_h2b)$full_result$level_cwc`), even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers. 
The results of the MLM are detailed in Table 1. 
`r table_1`
Differences between subjects could explain `r round((icc_h2b*100), digits = 0)` % of the total variance in SVs ($ICC =$ `r round(icc_h2b, digits = 2)`).
However, NFC had no statistically significant effect on SVs (`r apa_print(m1_h2b)$full_result$nfc_cgm`).
The simple slopes analysis revealed a significant difference in slope of n-back level for three different expressions of NFC (Table 2, Figure 2).
`r table_2`
`r h2c_ss.plot`
The Johnson-Neyman plot (Figure 2) visualizes the significance of the slope of n-back level at different values of NFC.
The Johnson-Neyman interval is [`r h2c_jn.int`].
Consequently, the slope of n-back level was not significant for individuals with very low NFC values.    
`r h2c_jn.plot`

## alternative: `r h2b_jn`

@@

The $AxAUC$ value did not predict any amount of variance in individual NFC scores (`r apa_print(hypothesis3a)$statistic$modelfit$r2`, `r apa_print(hypothesis3a)$estimate$modelfit$r2`).

@@

When including the AUC of all NASA-TLX subscales as a predictor, it could explain variance in NFC beyond the one (not) explained by the SVs (`r apa_print(hypothesis3b)$statistic$modelfit$r2`, `r apa_print(hypothesis3b)$estimate$modelfit$r2`).
An increase in one NASA-TLX AUC value corresponded, on average, to a decrease of `r round(hypothesis3b$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3b)$estimate$h3_data_auc_ntlx`).

@@

# Discussion

# (summary and interpretation of h2b_results)

@@

@@

@@

`r h2b_ss.table`
`r h2b_ss.plot`

>>>>

---
title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
shorttitle        : "The CERED paradigm for estimating subjective values"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1,*"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1,*"
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - original draft preparation
      - Writing - review & editing
      - Visualization
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote: |
  * Shared first authorship
abstract: |
  When individuals set goals, they consider the subjective value (SV) of both the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  However, the SV of effort is highly individual, and previous quantification approaches have had two crucial limitations: They presumed a unidirectional relationship between objective task load and the SV of effort, and as a consequence, they could only quantify the SVs of tasks with an objective order of task load.
  One of these approaches is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013).
  We aim to replicate their analysis with our adaptation, the Cognitive and Emotion Regulation Effort Discounting (CERED) paradigm.
  We argue that the CERED paradigm allows two crucial things: Quantifying SVs without assuming that the easiest level is preferred, and quantifying SVs for tasks with no objective order of task load.

@@

Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing n-back level, (1b) reaction time increases with increasing n-back level, and (1c) perceived task load increases with increasing n-back level.
Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
Here we added they hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.

@@

The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021].

@@

@@

@@

@@

@@

  # save plot
  Figure3 <- h2c_jn$plot

  # create interaction plot
  Figure2 <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                               plot.points = T, point.shape = T,
                               x.label = "n-back level", y.label = "subjective value",
                               legend.main = "NFC", interval = T) + theme_apa() +
    scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))

@@

@@

@@

We collected data from $N = 15$ participants.
One participant's NASA-TLX data is incomplete due to a technical error, so hypotheses 1c and 3b are analyzed using the 14 complete data sets.
The results showed increases in subjective and objective task load measures with higher n-back level.
Importantly, SVs were lower for higher n-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
The MLM revealed that n-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers.
And finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the AUC of NASA-TLX scores did.
All results are detailed in the *Supplementary Material*.

@@

@@

JZ and CS conceptualized the study and its methodology, acquired funding, investigated, administered the project, and wrote the software.
JZ and CK did the formal analysis, visualized the results, and prepared the original draft.
All authors reviewed, edited, and approved the final version of the manuscript.

@@

*Fig.1* Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.

*Fig.2* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.

@@

`r h2b_ss.table`

`r Figure2`
*Fig.2* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.
